Flatiron analysis

### 2021-09-09 Rmd/Report 2021.Rmd
Update clinical cleaning and creatinine
Add more drug cleaning, plots, tables in rmd

***
# I.Analysis Clinical

For all these analysis, I excluded the patients Lauren said to remove from the analysis.

@@

```{r loadd}
loadd(clinical_data, vitals, drugs, auc, creatinine)
Frontline <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Frontline.rds")
```

## 1.Clinical summary table
```{r analysis_data}

Treatment %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude == "1") %>%
  nrow()

analysis_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

library(naniar)
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

@@

analysis_data %>% filter(!is.na(target_auc) & !is.na(expected_dose)) %>%
    distinct(patientid, .keep_all = TRUE) %>% nrow()

# How should I filter??????????????????///
analysis_data %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

@@

@@

           "bmi", bmi_cat, "BSA",

@@

<div class = "row">
<div class = "col-md-6">
```{r clinical from dx, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

>>>>

@@

```{r loadd}
loadd(drugs)
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
```

At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.

# I. Drug episode questions

```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()

drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()
drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()
```

Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded

```{r}
drugs1 <- drugs1 %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )
drugs1 %>% distinct(patientid) %>% nrow()
```

60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
```{r}
remove_60daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
  distinct(patientid)
remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")

drugs1 <- drugs1 %>% 
  # remove these patients who 60 days rule
  filter(!str_detect(patientid, remove_60daysrule))

drugs1 %>% distinct(patientid) %>% nrow()
```

Remove linename that doesn't include platin or taxels -> later, need to recode linenumber first
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_drug < 60 | days_at_surg < 60) &
#            
#            days_at_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

drugs1 %>% 
  filter(linenumber == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```

```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route,
            diagnosisdate)) %>%

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_drug, days_at_surg) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  purrr::keep(~!all(is.na(.))) %>%
  ungroup() %>% 
  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

  mutate(drugname_type = case_when(
    str_detect(drugname, "platin")       ~ "platin",
    str_detect(drugname, "taxel")        ~ "taxel"
  ))
```

Recode linenumber depending on surgery date
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>%

  # 6.Add a 30 day rule to switch linenumber----
  # group_by(patientid, linenumber_new) %>% 
  # arrange(episodedate) %>% 
  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  # ungroup() %>% 
  # group_by(patientid) %>% 
  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new"), as.factor))

# Number of patient with a jump line in the first line # 60 would have
# therapy_line %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   arrange(desc(jump_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(jump_line) %>% 
#   tbl_summary()
```

# Number of patient who switch line because of surgery from line 1 to adjuvant line
```{r line coding}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```

# How many lines patient got as Neo
```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5) %>% 
  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
         drugname, episodedate, surgerydate, chemotherapy_type) %>%
  arrange(patientid, episodedate)
```

# Remove patients with more than 1 line as Neo -34
```{r}
remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, remove_morethan1_neo))

therapy_line %>% distinct(patientid) %>% nrow()
```

# Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Car") &
           drugname == "cisplatin") %>%
  distinct(patientid) %>% nrow()

therapy_line %>% 
  filter(str_detect(linename, "Cisplatin") &
           drugname == "carboplatin") %>%
  distinct(patientid) %>% nrow()

remove_switch <- therapy_line %>% 
  filter(
    (str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
  (str_detect(linename, "Cisplatin") & drugname == "carboplatin")
  ) %>%
  distinct(patientid)
remove_switch <- paste(remove_switch$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # remove these patients who switched C > C 
  filter(!str_detect(patientid, remove_switch))
therapy_line %>% distinct(patientid) %>% nrow()
```

Should I do the same between paclitaxel and docetaxel? Remember I pacli == pacli protein bound

If a patient had carbo, pacli, carbo, pacli, docetaxel in a Cabo-Pacli line : Could be annoying when I code cycle

In 1 cycle we can have taxel multiple times, is it possible for carbo or cisplatin?
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Pacli") &
           drugname == "docetaxel") %>%
  distinct(patientid) %>% nrow()
therapy_line %>% 
  filter(str_detect(linename, "Doce") &
           drugname == "Paclitaxel") %>%
  distinct(patientid) %>% nrow()
```

# Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

  arrange(patientid, episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
  mutate(cycle_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_drugname) %>%
  mutate(cycle_inc = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------

  # + What to do when it is a cycle change F003F2BEEDB37 ,

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_inc) %>% 
  group_by(patientid, linenumber_new) %>%
  mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%

  group_by(patientid, linenumber_new) %>% 
  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days

  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  mutate(n = row_number(drugname)) %>%

  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  fill(base_days_between_cycle, .direction = "downup") %>% 
  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  group_by(patientid, linenumber_new) %>%
  mutate(drug_count_perline = n()) %>%
  mutate(skipped_cycle_indays1 = ifelse(
    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  group_by(patientid) %>% 
  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
```

## Bind everything together and calculating target_auc and expected dose

When I bind things together I take the closest date of BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

  # Merge with height
  left_join(. , height,  by = "patientid") %>%
  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
           duration(n=1, unit="days"))) %>%
  arrange(interval_height) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # Calculate CrCl
  # inner_join(., clinical_data %>% select(-c("diagnosisdate", "surgerydate")),
  #            by = "patientid") %>% 
  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>%

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

```{r plot interval}
Treatment %>% 
  ggplot(aes(x= interval_creat)) +
  geom_bar() +
  coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_height)) +
  geom_bar() +
  coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_weight)) +
  geom_bar() +
  coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_bsa)) +
  geom_bar() +
  coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_auc)) +
  geom_bar() +
  coord_cartesian(ylim=c(0,50))
```

# Number of patients
```{r}
Treatment %>% distinct(patientid) %>% nrow()
```

Number of line in neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of line in Adj neo + surg + adj
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in Adj surg + adj
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Chemotherapy only") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```

# Final dataset
```{r analysis_data}
analysis_data <- Treatment %>% 
  # distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

After excluding exclude == "1" patients, we have `r analysis_data %>% distinct(patientid) %>% nrow()` patients.

```{r}
library(naniar)
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

@@

# analysis_data %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
If we remove patients who have at least 1 missing amount administrered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

# CALCULATE RDI

```{r}
Frontline <- Treatment %>% 
  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
  # group_by(patientid, linenumber_new, cycle_increment, drugname) %>% # ! -----------------------Change drugname if combine taxel....
  # mutate(amount_cycle = sum(amount)) %>% 
  # select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
  #        target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
  # ungroup() %>% 
  # distinct(patientid, linenumber_new, cycle_increment, drugname, .keep_all = TRUE) %>%

  # Create a linenumber restating at 1 for adj to be able to calculate RDI for first line of Adjuvant
    group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
  mutate(relative_dose_intensity = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ amount/expected_dose,
    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
  )) %>%
  # select(patientid, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by taxel or platin by line (will combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>%

  # Then let's see if we need to average that for the whole Neo BUT 
  # For now average rdi over whole neo, average rdi for the first line over adjuvant
  # when plot meed 1 rdi per drugname_type per chemotherapy_type aka distinct(patientid, chemotherapy_type, drugname_type)

  # group_by(patientid, chemotherapy_type, drugname_type) %>% 
  # mutate(RDI_neo = case_when(
  #   # chemotherapy_type == "Adjuvant"       ~ first(mean_RDI_per_drug_line), # F002B429BE6C6
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line),
  #   chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
  # )) %>%

  # mutate(RDI_adj = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line), # F002B429BE6C6
  #   # chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
  # )) %>% 
  # mutate(RDI = coalesce(RDI_neo, RDI_adj))

  # group_by(patientid, chemotherapy_type, drugname) %>% # ------------------------ Or should I do by cycle, then avg again
  # mutate(mean_RDI_per_drug_chemotype = mean(relative_dose_intensity)) %>% 
  # ungroup() %>% 
  mutate(RDI_grp = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.85) ))) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("1", "0"), 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("3", "0", "1","2","4", "5"), 
                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
  #   treatment_sequence == "Surgery only"                  ~ surgerydate
  # )) %>% 
  group_by(patientid) %>% 
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
                                          duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup() %>% 
  # %>% 
  # select(patientid, linenumber_new, drugname, surgerydate, episodedate, treatment_sequence, first_treatment_date, month_at_os_from_treatment)
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days"), 
         thirty_days_exclusion = ifelse(thirty_days_exclusion <= 30, "Exclude", NA_character_))

```

# Analysis

## 1.Clinical summary table

# How should I filter??????????????????///
analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, 
           agecat, "ageatdx",

@@

           "histology", "stagecat",

@@

           "bmi_at_dx", bmi_cat, "BSA",

@@

<div class = "row">
<div class = "col-md-6">
```{r clinical from dx, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
